Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-02-26 paper.tex
Random Forest description

In addition, in order to reduce the dimensionality of the input data and to choose an 
appropriate set of variables, the SOM \cite{kohonen1998} method has been also applied.

SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organisation, configures the output units into a topological representation of the original data. It tries to imitate the self-organisation done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus. SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organise data so as to disclose so far unknown patterns or structures. It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem. The main property of the SOM is that it makes a nonlinear projection from a high-dimensional data space (one dimension per variable) on a regular, low-dimensional (usually 2D) grid of neurons, called units.
SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons. It allows us to visualise any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure. High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.

SOMs (and U-Matrix) are usually applied to visualise natural structures in the data and their relations, as well as the natural groupings that could be among them. In addition, SOM makes easy the estimation of the variables that have more influence on these groupings. Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.
%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?

@@

As far as the feature selection methods are concerned, Weka separates the process into two parts:
%FERGU: por qué mencionamos a Weka aquí y no antes?
\begin{itemize}
  \item Attribute evaluator: This is the method by which the feature subsets are assessed. In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method are used.

@@

@@

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item \emph{Multilayer Perceptron}:
A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
artificial neural network model that maps the input data onto an appropriate output. 
It is an artificial neural network generally used for classification or 
approximation problems.

This model is a generalisation of the standard linear perceptron that uses several 
layers of nodes (called neurons) and that is able to solve linearly inseparable 
problems \cite{SteinwenderBitzer2003}.
Each neuron consists of a linear combination of weighted inputs which is passed 
though a non-linear activation function to produce its output.

This kind of artificial neural network is trained using a supervised learning 
technique called back-propagation.
This training method was developed independently by Werbos \cite{Werbos1974}, 
Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
in updating the weights of the output layer neurons once the erroneous output 
has been obtained, and then, propagating the successive weight layers back to 
the input layer.

A key issue when designing an MLP is the number of hidden layers of neurons.
Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
create classifying regions of any kind. This result was then confirmed in later 
works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.

>>>>

In addition, in order to reduce the dimensionality of the input data and to choose an appropriate set of variables, the Self-Organizing Map (SOM) \cite{kohonen1998} method has been also applied.

Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organisation, configures the output units into a topological representation of the original data. It tries to imitate the self-organisation done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus. SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organise data so as to disclose so far unknown patterns or structures. It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem. The main property of the SOM is that it makes a nonlinear projection from a high-dimensional data space (one dimension per variable) on a regular, low-dimensional (usually 2D) grid of neurons, called units.
SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons. It allows us to visualise any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure. High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.

SOMs (and U-Matrix) are usually applied to visualise natural structures in the data and their relations, as well as the natural groupings that could be among them. In addition, SOM makes easy the estimation of the variables that have more influence on these groupings. Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.
%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
% Antonio - arreglado

@@

As far as the feature selection methods are concerned, Weka software separates the process into two parts:
%FERGU: por qué mencionamos a Weka aquí y no antes?
% Antonio - se ha mencionado, pero sí, habría que destacarlo un poco más desde la intro quizá.
\begin{itemize}
  \item Attribute evaluator: This is the method by which the feature subsets are assessed. In this work, both a correlation-based feature subset evaluation method ({\tt CfsSubsetEval}) and an adaptation of relief for attribute estimation ({\tt ReliefFAttributeEval}) evaluation method are used.

@@

 \item \emph{Random Forest}: This method is based in the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution.
The result is the average of the generated trees during the process.

@@

% Antonio - MLP no se ha aplicado al final...

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
% \item \emph{Multilayer Perceptron}:
%A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
%artificial neural network model that maps the input data onto an appropriate output. 
%It is an artificial neural network generally used for classification or 
%approximation problems.
%
%This model is a generalisation of the standard linear perceptron that uses several 
%layers of nodes (called neurons) and that is able to solve linearly inseparable 
%problems \cite{SteinwenderBitzer2003}.
%Each neuron consists of a linear combination of weighted inputs which is passed 
%though a non-linear activation function to produce its output.
%
%This kind of artificial neural network is trained using a supervised learning 
%technique called back-propagation.
%This training method was developed independently by Werbos \cite{Werbos1974}, 
%Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
%in updating the weights of the output layer neurons once the erroneous output 
%has been obtained, and then, propagating the successive weight layers back to 
%the input layer.
%
%A key issue when designing an MLP is the number of hidden layers of neurons.
%Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
%create classifying regions of any kind. This result was then confirmed in later 
%works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
